\documentclass[erratum,amsmath,amssymb,aps, prb,showkeys]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{tabularx}
\usepackage{fullpage,subfigure,float,psfrag,textcomp,gensymb,tikz,siunitx}
\usepackage{booktabs,multirow, dcolumn}% Align table columns on decimal point
\usepackage{xspace}
\usepackage[bookmarks=true,pdftoolbar=true]{hyperref}
\hypersetup{%
  pdftitle = {MAX Phases: Cluster expansion},
  pdfkeywords = {pdf, hyperref, bookmarks},
  pdfauthor = {Anjana Talapatra}}
 \usepackage[all]{hypcap} 

\def\etal{\mbox{\it et al.\ }} 
\newcommand{\eq}[1]{Eq.~\ref{#1}}
\newcommand{\fig}[1]{Fig.~\ref{#1}}
\newcommand{\tab}[1]{TABLE~\ref{#1}}

\begin{document}

\title{A high throughput combinatorial study of the effect of M site alloying on the solid solution behavior of M\texorpdfstring{$_2$}{}AlC MAX phases}
	\author{Anjana Talapatra$^{1}$}
	\email{anjanatalapatra@tamu.edu}
	\author{T. Duong$^{1}$}
	\author{W. Son$^{1}$}
	\author{H. Gao$^{1}$}
	\author{M. Radovic$^{1,2}$}
	\author{R. Arr\'{o}yave $^{1,2}$}
	\affiliation{$^{1}$ Department of  Materials Science \& Engineering, TAMU, USA, 77843}
	\affiliation{ $^{2}$ Department of Mechanical Engineering, TAMU, USA, 77843}
	\date{\today}

\maketitle

In this Erratum, we correct some typographical errors that were overlooking during editing.
In the text, the following corrections are to be applied:

FIG.9 Caption: Calculated electronic density of states (DOS) for (a) Mn$_2$AlC and (b) (Ti$_{0.5}$,V$_0.5$)$_2$AlC. Red, blue and green colors indicate the contributions of the d, s, and p orbitals, respectively. The top panels indicate the total and orbital projected density of states, while the middle and lower panels indicate the site-projected density of states. (a) Mn$_2$AlC. (b) (Ti$_{0.5}$Mn$_{0.5}$)$_2$AlC. should read:

Calculated electronic density of states (DOS) for (a) Mn$_2$AlC and (b) (Ti$_{0.5}$Mn$_{0.5}$)$_2$AlC. Red, blue and green colors indicate the contributions of the d, s, and p orbitals, respectively. The top panels indicate the total and orbital projected density of states, while the middle and lower panels indicate the site-projected density of states. (a) Mn$_2$AlC. (b) (Ti$_{0.5}$Mn$_{0.5}$)$_2$AlC.


FIG.12 Caption: Calculated electronic density of states (DOS) for (a) Zn$_2$AlC and (b) (Ti$_0.5$,V$_0.5$)$_2$AlC. Red, blue, and green colors indicate the contributions of the d, s, and p orbitals, respectively. The top panels indicate the total and orbital projected density of states, while the middle and lower panels indicate the site-projected density of states. (a) Zn$_2$AlC. (b) (Ti$_{0.5}$Zn$_{0.5}$)$_2$AlC. should read:

Calculated electronic density of states (DOS) for (a) Zn$_2$AlC and (b) (Ti$_{1/3}$Zn$_{2/3}$)$_2$AlC. Red, blue, and green colors indicate the contributions of the d, s, and p orbitals, respectively. The top panels indicate the total and orbital projected density of states, while the middle and lower panels indicate the site-projected density of states. (a) Zn$_2$AlC. (b) (Ti$_{1/3}$Zn$_{2/3}$)$_2$AlC.

In Section IV.A.3, Page 104106-7, the second sentence 'The system is seen to favor ordering at the (Ti$_{1/3}$V$_{2/3}$)$_2$AlC  composition.' should read: The system is seen to favor ordering at the (Ti$_{1/3}$Zn$_{2/3}$)$_2$AlC composition.

These errors are only typographical in nature, and in the context of the results, can be easily spotted. The results presented and conclusions drawn are unaffected by the typographical errors.

\end{document}
%------------------------------------------------------------------------------------------------------------------------------------%