\documentclass[12pt]{article}
\usepackage[utf8x]{inputenc}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{setspace}
\usepackage{times, xcolor,graphicx}

\begin{document}
%-----------------------------------------------------------------
\begin{spacing}{1.24}

We would like to thank the reviewers of Calphad for considering our paper for submission, and giving us valuable suggestions in order to do so. We have complied with the suggestions given to us, and here is the summary of the improvements we have made to the paper.\\
%%--------------------------------------------------------------------------------------------------------------
\textbf{Reviewer \#1:} \\
%%--------------------------------------------------------------------------------------------------------------
The revision was performed carefully. As a minor point, the authors are asked to INCLUDE their response to topic 4 (arc melting) in the revised manuscript:
"From our experience on arc-melting of CoNiGa, usually Ga loss is around 3\% of all
Ga. Therefore, some extra Ga is added ( 3\% more) to have a composition very close
to target composition. Our WDS analyses confirmed that the measured compositions
are very close to nominal compositions. We have water cooled Cu crucible. We dont
expect any reaction with Ga. Most importantly, Ga is added on top of other elements
to minimize any reaction with crucible.In addition, we did not see any indication of
a reaction on the crucible surface after melting."
This information is valuable for the readers, enhancing the relatively brief experimental description. 

After that minor correction the paper is is highly recommended for publication. \\
%%--------------------------------------------------------------------------------------------------------------
Response : \textcolor{red}{ The paragraph above has been added to the manuscript in section 4 and is highlighted in red.}
\end{spacing}

\end{document}
